---
title: "wildlifeTG: Methods for Time Geographic Home Range Analysis"
author: "Jed Long"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The wildlifeTG package provides access to functions for time geographic analysis of wildlife telemetry data. Specifically, the methods are targeted at home range analysis and related ideas.

The methods are described in the following papers:

Long, J.A. (2018) Modelling movement probabilities within heterogeneous spatial fields. Journal
of Spatial Information Science. Accepted: 2017-12-18.

Long, J.A., Webb, S.L., Nelson, T.A., Gee, K. (2015) Mapping areas of spatial-temporal
overlap from wildlife telemetry data. Movement Ecology. 3:38.

Long, J.A., Nelson, T.A. (2015) Home range and habitat analysis using dynamic time
geography. Journal of Wildlife Management. 79(3): 481-490.

Nelson, T.A., Long, J.A., Laberee, K., Stewart, B.P. (2015) A time geographic approach for
delineating areas of sustained wildlife use. Annals of GIS. 21(1): 81-90.

Long, J.A., Nelson, T.A. (2012) Time geography and wildlife home range delineation.
Journal of Wildlife Management. 76(2): 407-413.

##Installation

Currently, installation is only supported via GitHub, may put it on CRAN eventually.

```{r installation, eval = TRUE, message = FALSE, warning = FALSE}
devtools::install_github("jedalong/wildlifeTG")
```

##Telemetry Data for Examples

A small dataset showing the movement of a caribou

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
